```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
DF <- DF %>% 
  filter(spot_dx == "Invasive") %>% 
  droplevels()

x <- DF$PAICS_ext_max

```

\   

# By maximum PAICS extent {.tabset .tabset-pills .tabset-fade}
## Clinical features {.tabset .tabset-pills .tabset-fade}
### Age
```{r age_group.marker}
y <- DF$age_group
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Sex
```{r sex.marker}
y <- DF$sex
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Race
```{r race.marker}
y <- DF$race
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

## Pathologic features {.tabset .tabset-pills .tabset-fade}
### Pathologic stage
```{r stage_pt.marker}
y <- DF$stage_pt
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Clinical stage
```{r stage_clinical.marker}
y <- DF$stage_clinical
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Adjacent CIS
```{r cis.marker}
y <- DF$cis
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Lymphovascular invasion
```{r lvi.marker}
y <- DF$lvi
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Lymph node metastasis
```{r metastasis_lymphnodes.marker}
y <- DF$metastasis_lymphnodes
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

## Outcome features {.tabset .tabset-pills .tabset-fade}
### Tumor progression
```{r progression.marker}
y <- DF$progression
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Visceral metastasis
```{r metastasis_visceral.marker}
y <- DF$metastasis_visceral
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Overall mortality
```{r dead.marker}
y <- DF$dead
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```

### Cancer-related mortality
```{r dod.marker}
y <- DF$dod
g2_nice(x, y)
tbl_nice(x, y)
tbl_test(x, y)
```
