```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
```

\   

# Clinicopathologic and outcome features {.tabset .tabset-pills .tabset-fade}
## Clinical features {.tabset .tabset-pills .tabset-fade}
### Age
```{r age}
x <- DF$age
g_nice(x, max_break = 90)
tbl_nice(x)
```

### Sex
```{r sex}
x <- DF$sex
g_nice(x)
tbl_nice(x)
```

### Race
```{r race}
x <- DF$race
g_nice(x)
tbl_nice(x)
```

## Pathologic features {.tabset .tabset-pills .tabset-fade}
### Diagnosis
```{r spot_dx}
x <- DF$spot_dx
g_nice(x)
tbl_nice(x)
```

### pT stage
```{r stage_pt}
x <- DF$stage_pt
g_nice(x)
tbl_nice(x)
```

### Clinical stage
```{r stage_clinical}
x <- DF$stage_clinical
g_nice(x)
tbl_nice(x)
```

### Histologic grade
```{r grade}
x <- DF$grade
g_nice(x)
tbl_nice(x)
```

### CIS
```{r cis}
x <- DF$cis
g_nice(x)
tbl_nice(x)
```

### Lymphovascular invasion
```{r lvi}
x <- DF$lvi
g_nice(x)
tbl_nice(x)
```

### Lymph node metastasis
```{r metastasis_lymphnodes}
x <- DF$metastasis_lymphnodes
g_nice(x)
tbl_nice(x)
```

## Preoperative features {.tabset .tabset-pills .tabset-fade}
### Preop CIS
```{r preop_cis}
x <- DF$preop_cis
g_nice(x)
tbl_nice(x)
```

### Preop procedure
```{r preop_procedure}
x <- DF$preop_procedure
g_nice(x)
tbl_nice(x)
```

### Preop stage
```{r preop_stage}
x <- DF$preop_stage
g_nice(x)
tbl_nice(x)
```

## Treatment features {.tabset .tabset-pills .tabset-fade}
### Preop RTx
```{r preop_rtx}
x <- DF$preop_rtx
g_nice(x)
tbl_nice(x)
```

### Preop CTx
```{r preop_chemo}
x <- DF$preop_chemo
g_nice(x)
tbl_nice(x)
```

### Intravesical CTx
```{r intravesical_chemo}
x <- DF$intravesical_chemo
g_nice(x)
tbl_nice(x)
```

### Intravesical CTx type
```{r intravesical_chemo_type}
x <- DF$intravesical_chemo_type
g_nice(x)
tbl_nice(x)
```

### Postop RTx
```{r postop_rtx}
x <- DF$postop_rtx
g_nice(x)
tbl_nice(x)
```

### Postop CTx
```{r postop_chemo}
x <- DF$postop_chemo
g_nice(x)
tbl_nice(x)
```

### Postop CTx type
```{r postop_chemo_type}
x <- DF$postop_chemo_type
g_nice(x)
tbl_nice(x)
```

## Outcome features {.tabset .tabset-pills .tabset-fade}
### Follow-up, in months
```{r fu_mo}
x <- DF$fu_mo
g_nice(x, bin = 24, max_break = 216)
tbl_nice(x)
```

### Tumor progression
```{r progression}
x <- DF$progression
g_nice(x)
tbl_nice(x)
```

### Visceral metastasis
```{r metastasis_visceral}
x <- DF$metastasis_visceral
g_nice(x)
tbl_nice(x)
```

### Overall mortality
```{r dead}
x <- DF$dead
g_nice(x)
tbl_nice(x)
```

### Cancer-related mortality
```{r dod}
x <- DF$dod
g_nice(x)
tbl_nice(x)
```

