```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global_672.R")
```

\   

# Marker features {.tabset .tabset-pills .tabset-fade}
## By TMA spots {.tabset .tabset-pills .tabset-fade}
### Marker extent
```{r PAICS_extent}
x <- marker$PAICS_extent
g_nice(x, bin = 10)
tbl_nice(x)
```

### Marker intensity
```{r PAICS_intensity}
x <- marker$PAICS_intensity
g_nice(x)
tbl_nice(x)
```

### Marker H-score
```{r PAICS_h}
x <- marker$PAICS_h
g_nice(x, bin = 25)
tbl_nice(x)
```

***

## By SP cases {.tabset .tabset-pills .tabset-fade}
### Summarizing by the median value {.tabset .tabset-pills .tabset-fade}
#### Marker extent
```{r PAICS_ext_med}
x <- DF$PAICS_ext_med
g_nice(x, bin = 10)
tbl_nice(x)
```

#### Marker intensity
```{r PAICS_int_med}
x <- factor(DF$PAICS_int_med)
g_nice(x)
tbl_nice(x)
```

#### Marker H-score
```{r PAICS_h_med}
x <- DF$PAICS_h_med
g_nice(x, bin = 25)
tbl_nice(x)
```

### Summarizing by the maximum value {.tabset .tabset-pills .tabset-fade}
#### Marker extent
```{r PAICS_ext_max}
x <- DF$PAICS_ext_max
g_nice(x, bin = 10)
tbl_nice(x)
```

#### Marker intensity
```{r PAICS_int_max}
x <- factor(DF$PAICS_int_max)
g_nice(x)
tbl_nice(x)
```

#### Marker H-score
```{r PAICS_h_max}
x <- DF$PAICS_h_max
g_nice(x, bin = 25)
tbl_nice(x)
```
