```{r Global, echo=FALSE, warning=FALSE, message=FALSE}
source("Global.R")
DF <- DF %>% 
  filter(spot_dx == "Invasive") %>% 
  droplevels()

FU <- DF$fu_mo

```

\   

# Survival curves {.tabset .tabset-pills .tabset-fade}
## Tumor progression {.tabset .tabset-pills .tabset-fade}
### By extent {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_ext_level_0.progression}
outcome <- DF$progression
status <- DF$PAICS_ext_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_ext_level_med.progression}
status <- DF$PAICS_ext_level_med
g_surv(FU, outcome, status)
```

### By intensity {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_int_level_0.progression}
status <- DF$PAICS_int_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_int_level_med.progression}
status <- DF$PAICS_int_level_med
g_surv(FU, outcome, status)
```

### By H-score {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_h_level_0.progression}
status <- DF$PAICS_h_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_h_level_med.progression}
status <- DF$PAICS_h_level_med
g_surv(FU, outcome, status)
```

## Overall mortality {.tabset .tabset-pills .tabset-fade}
### By extent {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_ext_level_0.dead}
outcome <- DF$dead
status <- DF$PAICS_ext_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_ext_level_med.dead}
status <- DF$PAICS_ext_level_med
g_surv(FU, outcome, status)
```

### By intensity {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_int_level_0.dead}
status <- DF$PAICS_int_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_int_level_med.dead}
status <- DF$PAICS_int_level_med
g_surv(FU, outcome, status)
```

### By H-score {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_h_level_0.dead}
status <- DF$PAICS_h_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_h_level_med.dead}
status <- DF$PAICS_h_level_med
g_surv(FU, outcome, status)
```

## Cancer-related mortality {.tabset .tabset-pills .tabset-fade}
### By extent {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_ext_level_0.dod}
outcome <- DF$dod
status <- DF$PAICS_ext_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_ext_level_med.dod}
status <- DF$PAICS_ext_level_med
g_surv(FU, outcome, status)
```

### By intensity {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_int_level_0.dod}
status <- DF$PAICS_int_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_int_level_med.dod}
status <- DF$PAICS_int_level_med
g_surv(FU, outcome, status)
```

### By H-score {.tabset .tabset-pills .tabset-fade}
#### Cutoff point: 0
```{r PAICS_h_level_0.dod}
status <- DF$PAICS_h_level_0
g_surv(FU, outcome, status)
```

#### Cutoff point: median
```{r PAICS_h_level_med.dod}
status <- DF$PAICS_h_level_med
g_surv(FU, outcome, status)
```

